\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{prezi_ch}
Aportaciones de los Chinos a las Matemáticas\\
  \url{https://prezi.com/5xzrxewmjjxo/aportaciones-de-los-chinos-a-las-matematicas/}

\bibitem{wiki_ch_mat}
Chinese Mathematics. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Chinese_mathematics}

\bibitem{sm_ch}
El Sistema de Numeración Chino. Sector Matemática.\\
  \url{http://www.sectormatematica.cl/historia/chino.htm}

\bibitem{uco_ch}
Sistema de Numeración Multiplicativo de China. Universidad de Córdoba.\\
  \url{http://www.uco.es/users/ma1fegan/2010-2011/md/Temas/Tema-1/Sistema-de-numeracion-China.pdf}

\bibitem{wiki_suanpan}
Suanpan. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Suanpan}
  
\bibitem{wiki_JiuzhangSuanshu}
The Nine Chapters on the Mathematical Art. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/The_Nine_Chapters_on_the_Mathematical_Art}  
  
\bibitem{mp_LiuHui}
LIU HUI. Matematicas Proyecto.\\
  \url{http://trabajodematematicascambridgeschool.blogspot.com.es/2014/03/liu-hui.html}

\bibitem{mi_LiuHui}
Liu Hui. math.info\\
  \url{http://apprendre-math.info/espagnol/historyDetail.htm?id=Liu_Hui}
  
\bibitem{wiki_LiuHui}
Liu Hui. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Liu_Hui}
  
\bibitem{uaq_ZuChongzhi}
Bibliografía de Zu Chongzhi. Universidad Autónoma de Querétaro(México).\\
  \url{http://www.uaq.mx/ingenieria/publicaciones/eureka/n24/chongzhi.pdf}

\bibitem{wiki_ZuChongzhi}
Zu Chongzhi. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Zu_Chongzhi}
  
\bibitem{byv_QinJiushao}
Qin Jiushao. Bibliografias y vidas.\\
  \url{http://www.biografiasyvidas.com/biografia/q/qin_jiushao.htm}

\bibitem{St.A_QinJiushao}
Qin Jiushao. School of Mathematical and Computational Sciences, University of St Andrews.\\
  \url{http://www-groups.dcs.st-and.ac.uk/history/Biographies/Qin_Jiushao.html}

\bibitem{wiki_QinJiushao}
Qin Jiushao. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Qin_Jiushao}

\bibitem{maa_ShiingShenChern}
Shiing-Shen Chern. Mathematical Association of America.\\
  \url{http://www.maa.org/news/in-memoriam-shiing-shen-chern-1911-2004}

\bibitem{wiki_ShiingShenChern}
Shiing-Shen Chern. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Shiing-Shen_Chern}

\bibitem{mo_ChenJingrun}
Chen Jingrun, un relevante matemático chino. Matemolivares.\\
  \url{http://matemolivares.blogia.com/2011/052201-chen-jingrun-un-relevante-matematico-chino..php}

\bibitem{wiki_ChenJingrun}
Chen Jingrum. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Chen_Jingrun}

\bibitem{wiki_ind_mat}
Indian Mathematics. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Indian_mathematics}

\bibitem{wiki_MultiplicaciónCelosía}
Multiplication Algorithm. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Multiplication_algorithm#Lattice_multiplication}

\bibitem{wiki_GalleyDivision}
Galley Division. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Galley_division}

\bibitem{mcnb_Aryabhata}
Aryabhata. La Web de las Bibliografías.\\
  \url{http://www.mcnbiografias.com/app-bio/do/show?key=aryabhata}

\bibitem{wiki_Aryabhata}
Aryabhata. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Aryabhata}

\bibitem{mt_Varahamihira}
Varahamihira. MacTutor History of Mathematics archive.\\
  \url{http://www-history.mcs.st-and.ac.uk/Biographies/Varahamihira.html}

\bibitem{wiki_Varahamihira}
Varahamihira. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Varahamihira}

\bibitem{mcnb_Brahmagupta}
Brahmagupta. La Web de las Bibliografías.\\
  \url{http://www.mcnbiografias.com/app-bio/do/show?key=brahmagupta}

\bibitem{wiki_Brahmagupta}
Brahmagupta. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Brahmagupta}

\bibitem{mcnb_Bhaskara_II}
Bhaskara II. La Web de las Bibliografías.\\
  \url{http://www.mcnbiografias.com/app-bio/do/show?key=bhaskarakarya}

\bibitem{mt_Bhaskara_II}
Bhaskara II. MacTutor History of Mathematics archive.\\
  \url{http://www-history.mcs.st-and.ac.uk/Biographies/Bhaskara_II.html}

\bibitem{wiki_Bhaskara_II}
Bhaskara II. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Bhaskara_II}
  
\bibitem{mt_Madhava}
Madhava de Sangamagrama. MacTutor History of Mathematics archive.\\
  \url{http://www-history.mcs.st-and.ac.uk/Biographies/Madhava.html}

\bibitem{wiki_Madhava}
Madhava de Sangamagrama. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Madhava_of_Sangamagrama}

\end{thebibliography}
